Interactive Visualization for System Log Analysis

### 2013-12-18 paper/paper.tex
Updated conclusion

We have presented a system for visualizing arbitrary log files.
The log files are automatically and distributedly parsed, features are computed per node, and the results are visualized in an easy-to-use web interface.
We cluster similarly-performing nodes into a single visualization to abstract away redundant data, if the user desires.

The visualization has a spectrum of parameters.
On one end of this spectrum, the raw log data is shown; on the other end, a single graph shows the most representative state of the system.
The importance of this point is \emph{trustworthiness} of the visualization: no data is hidden from the user.

Our visualization is still extremely primitive.
Users may have no intuition as to why two clusters are separated.
Displaying a cluster confidence may assist in telling the user when two clusters are not very different.
On the other hand, if two clusters should be different (such as in the case of a 1\% slowdown of a node), we would want to tell the user more information about why they were clustered differently.
As is, it would be very hard for a user to notice a 1\% slowdown in a node.

We would like to compute more elaborate features for the clustering, including higher-order statistics.
However, as the feature complexity increases, the interactivity decreases.
Finding a middle-ground between interactivity and complexity is an open problem which we are not sure how to address.

Finally, we would need a more thorough evaluation of our visualization.
Some questions we have are:
\begin{enumerate}
    \item is a scatterplot the best visualization choice?
    \item are we able to successfully segregate other types of anomalies in different clusters?
    \item can multiple messages be aggregated into the same plot?
\end{enumerate}

>>>>

We have presented a system for visualizing arbitrary log files.
The log files are automatically and distributedly parsed, features are computed per node, and the results are visualized in an easy-to-use web interface.
We cluster similarly-performing nodes into a single visualization to abstract away redundant data.

The visualization has a spectrum of parameters.
On one end of this spectrum, the raw log data is shown; on the other end, a single graph shows the most representative state of the system.
This is important to maintain \emph{trustworthiness} of the visualization: no data is hidden from the user.

Our visualization is still extremely primitive.
Users may have no intuition as to why two clusters are separated.
Displaying a cluster confidence may assist in telling the user when two clusters are not very different.
On the other hand, if two clusters should be different, we would want to provide an explanation to the user similar to the decision tree visualization of Xu and collaborators \shortcite{Xu09}.
As is, it would be very hard for a user to notice a 1\% slowdown in a node.

We would like to compute more representative features for the clustering, including higher-order statistics.
However, as the feature complexity increases, the interactivity decreases.
Finding a middle-ground between interactivity and complexity is an difficult problem: we must be able to compute all of the features without touching all of the data.

Finally, we would need a more thorough evaluation of our visualization.
Some questions we have are:
\begin{enumerate}
    \item is a scatterplot the best visualization choice?
    \item are we able to successfully segregate other types of anomalies in different clusters?
    \item can multiple messages be aggregated into the same plot?
    \item what additional information would assist the human in understanding the visualization?
\end{enumerate}
